\nocite{*}
\begin{thebibliography}{99}
\bibitem{machado-chaimowicz}
  Marcos C. Machado, Luiz Chaimowicz.
  Computer Science Department,
  Federal University of Minas Gerais,
  Belo Horizonte, Brazil.
  \emph{Combining Metaheuristics and CSP Algorithms to solve Sudoku}.
  
\bibitem{barlett-langville}
  Andrew C. Barlett, Amy N. Langville.
  Department of Mathematics,
  College of Charleston,
  Charlston, SC.
  \emph{An Integer Programming Model for the Sudoku Problem}.

\bibitem{lewis}
  Rhyd Lewis.
  Centre for Emergent Computing,
  Napier University, Scotland.
  \emph{Metaheuristics can Solve Sudoku Puzzles}.

\bibitem{variations}
  Ed Pegg Jr,
  2005/09/06.
  \emph{Sudoku Variations}.
  Acesso em Junho de 2013 à \url{http://www.maa.org/editorial/mathgames/mathgames_09_05_05.html}.

\bibitem{springer}
  J. Dréo, A. Pétrowski, E. Taillard.
  \emph{Metaheuristics for Hard Optimization} (2006).

\bibitem{wikiSAen}
  Wikipedia.
  \emph{Simulated Annealing}.
  Acesso em Junho de 2013 à \url{http://en.wikipedia.org/wiki/Simulated_annealing}.

\bibitem{wikiSApt}
  Wikipédia.
  \emph{Simulated Annealing ou Arrefecimento simulado}.
  Acesso em Junho de 2013 à \url{http://pt.wikipedia.org/wiki/Simulated_annealing}.

\bibitem{wikiMetropolisHastings}
  Wikipedia.
  \emph{Metropolis–Hastings algorithm}.
  Acesso em Junho de 2013 à \url{http://en.wikipedia.org/wiki/Metropolis-Hastings_algorithm}.

\bibitem{aula}
  Marcus Ritt, Luciana Buriol.
  \emph{INF05010 --- Otimização combinatória. Notas de aula}.
  2012/04/04.
\end{thebibliography}
